%-----------EXPERIENCE-----------%
\section{EXPERIENCE}
\resumeSubHeadingListStart

    \resumeSubheading
    {Algohire}{Aug 2023 -- Present}
    {Software Engineer}{Hyderabad}
    \resumeItemListStart
        \resumeItem{Joined \textbf{algohire.ai} as one of the core developers and among the earliest contributors to its development. \textbf{algohire.ai} is a pioneering platform designed to empower recruiters in filtering candidates based on advanced test scores and comprehensive resume analysis.}
        \resumeItem{Developed a feature enabling recruiters to upload bulk resumes and efficiently handle them with a web worker for improved performance. After uploading, provided comprehensive resume analysis including a resume score for each candidate.}
        \resumeItem{Implemented a subscription pricing module for recurring payments using \textbf{Razorpay}, offering both monthly and yearly billing options to users.}
        \resumeItem{Enabled candidates to take tests assigned by recruiters directly on the platform, with integrated proctoring to ensure test integrity.}
        \resumeItem{Utilized modern technologies including \textbf{React}, \textbf{Next.js}, \textbf{Node.js}, \textbf{Firebase SDK}, \textbf{AWS services}, and \textbf{Shadcn} to build a robust and scalable application.}
        \resumeItem{Enhanced platform efficiency and user experience, resulting in a 30\% increase in recruiter satisfaction and a 25\% reduction in candidate filtering time.}
        \resumeItem{Provided mentorship and leadership to a team of interns, fostering effective collaboration and driving project success.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Niiu Capital}{Mar 2023 -- Jul 2023}
    {Full Stack Web Developer Intern}{Singapore (Remote)}
    \resumeItemListStart
        \resumeItem{Developed a full-fledged web application for \textbf{singcapital}, a financial organization in Singapore, from the ground up.}
        \resumeItem{Designed and implemented the user interface using \textbf{Next.js} and \textbf{Tailwind CSS}, ensuring a seamless and responsive user experience.}
        \resumeItem{Integrated \textbf{Sanity CMS} into a React.js project, simplifying content management for blog and article writers.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
