%-----------PROJECTS-----------%
\section{PROJECTS}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Shoe Store} $|$ \emph{Next.js 13, Strapi CMS, Redux, Tailwind CSS}}    {\href{https://nike-clone-frontend-seven.vercel.app}{\textit{\textbf{Demo}}}}
    \resumeItemListStart
        \resumeItem {Developed a robust and scalable e-commerce website using Next.js 13 and Strapi CMS, emphasizing server-side rendering (SSR) and static site generation (SSG) for fast loading times and optimal SEO performance.}
        \resumeItem{Implemented dynamic routing to create seamless navigation and personalized user experiences.}
        \resumeItem{Demonstrated seamless integration of Strapi APIs with Next.js for fetching and displaying dynamic content on the frontend.}
        \resumeItem{Utilized Redux for state management, implementing complete cart functionality including adding, updating, and deleting items.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Social Developer Platform} $|$ \emph{React, Bootstrap, CSS, Redux, Node.js, Express.js}}    {\href{https://social-dev-connector.web.app/}{\textit{\textbf{Demo}}}}
    \resumeItemListStart
        \resumeItem {Built a social networking platform for developers, enabling users to create profiles, share posts, and connect with other developers.}
        \resumeItem{Developed the user interface using React and Bootstrap for a responsive and dynamic experience.}
        \resumeItem{Utilized Redux for state management, ensuring efficient data handling and state updates across the application.}
        \resumeItem{Implemented backend services using Node.js and Express.js, providing robust API endpoints for user authentication and data management.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
